SP

### 2018-03-26 SP_data_cleaning.Rmd
Spanish data

---
title: "SP"
author: "I. Bartomeus"
date: "05/10/2017"
output: html_document
---

@@

```{r}
sp <- read.csv(file = "raw_data/Spain.csv", h = T)
head(sp)
head(sort(table(sp$LOCALIDAD), decreasing = TRUE))
write.csv(sort(table(sp$LOCALIDAD), decreasing = TRUE),
          "raw_data/localidades.csv")

@@

#check sampling completness
library(vegan)
#need to fix first locality
comm <- table(sp2$LOCALIDAD, sp2$gen_sp)
temp <- specaccum(comm, "random")
summary(temp)
plot(temp)
rarecurve(comm)

@@

@@

>>>>

---
title: "SP"
author: "I. Bartomeus"
date: "05/10/2017"
output: html_document
editor_options: 
  chunk_output_type: console
---

@@

```{r}
sp <- read.csv(file = "raw_data/Spain.csv", h = T)
head(sp)
head(sort(table(sp$LOCALIDAD), decreasing = TRUE))
#write.csv(sort(table(sp$LOCALIDAD), decreasing = TRUE),
 #         "raw_data/localidades.csv")

@@

sp2 <- subset(sp, LOCALIDAD %in% c('"Finca Zamadue?as"',
                            "Toro",
                            "Granja Escuela Jose Antonio",
                            "Villab??ez",
                            '""Finca Zamadue?as""',
                            "Hornillos",
                            '"Camino Hondo" Granja Escuela Jose Antonio',
                            "Parc. 16 Granja Escuela Jose Antonio",
                            "Mojados",
                            "Coto Bajo Matallana",
                            "San llorente",
                            "San Llorente",
                            "_Finca Zamadue?as_",
                            "La Senovilla Olmedo",
                            "Coto Bajo de Matallana Villalba de los Alcores",
                            "Mojados",
                            "Olmedo",
                            "Coto Bajo Matallana Villalba de los Alcores",
                            "Las Fuentes Mojados",
                            "Paramo de Matallana",
                            "Villalba de los Alcores",
                            "_Coto Bajo de Matallana_",
                            "_Coto Bajo de Matallana_",
                            "Coto Bajo de Matallana Montealegre",
                            "Coto Bajo Matallana",
                            "Las Fuentes  Mojados",
                            "P?ramo de Matallana Villanubla",
                            "Olmedo"))

head(sp2)

sp2 <- droplevels(sp2)
levels(sp2$LOCALIDAD) <- c("zamaduenas",
                           "auditorio_Delibes", 
                           "zamaduenas",
                           "auditorio_Delibes",
                           "hornillos",
                           "olmedo",
                           "olmedo",
                           "auditorio_Delibes",
                           "sanbernardo",
                           "sanbernardo",
                           "toro",
                           "vilalba",
                           "vilalba")

#check sampling completness
library(vegan)
#need to fix first locality
head(sp2)
comm <- table(sp2$LOCALIDAD, sp2$gen_sp)
temp <- specaccum(comm, "random")
summary(temp)
plot(temp)
rarecurve(comm)

@@

```{r}
#make final dataset
sp3 <- sp2[,c("LOCALIDAD", "gen_sp", "NUM_EJEMPLARES")]
now3 <- now[, c("LOCALIDAD", "gen_sp")]
now3$NUM_EJEMPLARES <- 1
now3$when <- "now"
sp3$when <- "asensio"

library(lettercase)
str_ucfirst(str_lower_case(sp3$gen_sp[1:10]))

sp3$gen_sp <- str_ucfirst(str_lower_case(sp3$gen_sp))

dat <- rbind(sp3, now3)
#check stuff
head(dat)
unique(dat$gen_sp) #400
#this can be cleaned, but looks decent!

colnames(dat) <- c("locality", "gen_sp", "freq", "when")
unique(dat$locality) #400

write.csv(dat, "data/spain_clean.csv", row.names = F)
```

@@

1.1) Show raref per site
